---
title: "Aethelometer Dataset - Black Carbon Concentration in Air."
author: "Tarun"
date: "5/9/2021"
output: slidy_presentation
job: Reproducible Pitch Presentation
subtitle: Aethalometer

---
## Coursera Reproducible Pitch


## mtcars Dataset

### Motor Trend Car Road Tests

An Aethalometer is an instrument for measuring the concentration of optically absorbing (‘black’) suspended particulates in a gas colloid stream; commonly visualized as smoke or haze, often seen in ambient air under polluted conditions..
### Source
Dataset available here- https://data.europa.eu/data/datasets/jrc-abcis-ap-ebcae-2017?locale=en.

```{r,echo=TRUE}
data <- read.csv("Dec-2017.csv")

```
---

## Aethalometer Dataset - Format

**A data frame with 44504 observations on 68 variables.**
The Aethalometer is an absolute measurement based on sample flow, spot size, and optical attenuation. The sample flow is checked annually (see Section 12.0). Elemental carbon concentration is measured in µg/m3. The detection range of the Aethalometer is 0.1 to ~ 100 µg/m3.

```{r,echo=T}
colnames(data)
str(data)
````